Containers and R---the Rockerverse and beyond

### 2019-11-09 manuscript.Rmd
add kubernetes paragraph

- [`babelwhale`](https://cran.r-project.org/web/packages/babelwhale/index.html): Running a Docker from R with Singularity or Docker as back-end. This is really useful in HPC environments where a user might not have root access but is able to install Singularity instead of Docker. [@rcannood]
- `RSelenium`
- [`googleComputeEngineR`](https://cloudyr.github.io/googleComputeEngineR/) (function `gce_vm_template()`)
  - To enable quick deployments of key R services such as RStudio and Shiny onto cloud virtual machines (VMs), this package utilises Dockerfiles to move the labour of setting up those services from the user to a premade Docker image.  For example, by specifying the template `template="rstudio"` in `gce_vm_template()/gce_vm()` an up to date RStudio Service image is launched.  Specifying `template="rstudio-gpu"` will launch an RStudio Server image with a GPU attached, etc.  
- [`analogsea`](https://github.com/sckott/analogsea) (digital ocean R client)
- [`plumber`](https://www.rplumber.io/docs/hosting.html#docker)
- [production deployment of neural networks](https://github.com/tmobile/r-tensorflow-api) [@jnolis, @nolistic]

>>>>

- [`babelwhale`](https://cran.r-project.org/web/packages/babelwhale/index.html): Running a Docker from R with Singularity or Docker as back-end. This is really useful in HPC environments where a user might not have root access but is able to install Singularity instead of Docker. [@rcannood]
- `RSelenium`
- [`googleComputeEngineR`](https://cloudyr.github.io/googleComputeEngineR/) (function `gce_vm_template()`)
  - To enable quick deployments of key R services such as RStudio and Shiny onto cloud virtual machines (VMs), this package utilises Dockerfiles to move the labour of setting up those services from the user to a premade Docker image.  For example, by specifying the template `template="rstudio"` in `gce_vm_template()/gce_vm()` an up to date RStudio Service image is launched.  Specifying `template="rstudio-gpu"` will launch an RStudio Server image with a GPU attached, etc.  
- [`analogsea`](https://github.com/sckott/analogsea) (digital ocean R client)
- [`plumber`](https://www.rplumber.io/docs/hosting.html#docker)
- [production deployment of neural networks](https://github.com/tmobile/r-tensorflow-api) [@jnolis, @nolistic]
- Kubernetes - A popular platform for managing Docker containers is [Kubernetes](https://kubernetes.io/), which is used for a wide variety of containerized applications.  It may be your organisation has a Kubernetes cluster already for other applications.  Docker containers are used within Kubernetes clusters to hold native code, for which Kubernetes creates a framework around network connections and scaling of resources up and down.  An introduction on using [Kubernetes with R is published at this blog post](https://code.markedmondson.me/r-on-kubernetes-serverless-shiny-r-apis-and-scheduled-scripts/).
